


% generic
All my experiences collectively shaped my research interests and motivated me to enroll in a PhD program, where I can further develop my research career and pursue my goal of building more effective and responsible human-AI collaboration. 
% specific
University of Michigan's PhD program in Computer Science is appealing to me because of the department's strong AI and HCI research and the many faculty members whose interests align with mine. 
% faculty 1
I am interested in Professor Xu Wang's direction in building human-AI systems for education as it overlaps with my own interest in machine teaching. In her work \textit{Towards Process-Oriented, Modular, and Versatile Question Generation that Meets Educational Needs} [\citenum{Wang2022}], I liked the methodology of text replay enactment to elicit stakeholder needs and I would be interested in building human-AI collaborative QG systems.
% faculty 2
I also enjoyed Professor Elizabeth Bondi-Kelly's work \textit{Role of Human-AI Interaction in Selective Prediction} [\citenum{Bondi2022}] as it shows in HAI the importance of human cognitive factors, like communication of how human-AI collaborate and presenting AI decisions. Additionally, I am very curious to why showing deferral status improves human accuracy and I believe a deeper understanding of this may be crucial for human-AI collaboration. 
% faculty 3
I am also interested in Professor Anhong Guo's direction in human-AI interactive systems and AI fairness and Professor Lu Wang's work on NLP and AI for education.
% conclusion
My interests in HAI are well represented at University of Michigan, and I believe a PhD in Computer Science will foster my research skills and advance my goal of building more effective and responsible human-AI collaboration.
